---
title: "Comparison of length based idicators and methods"
subtitle: ""
author: "L Kell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
       includes:
            in_header: header.tex 
---


```{r, knitr, eval=TRUE, echo=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo=FALSE)

library(knitr)

opts_chunk$set(comment   =NA, 
               warning   =FALSE, 
               message   =FALSE, 
               error     =FALSE, 
               echo      =FALSE,
               fig.width =8, 
               fig.height=6,
               cache     =TRUE, 
               fig.path  ="figs/",
               cache.path="cache/figs/",
               dev        =c("png"))

iFig=0
iTab=0
```

\newpage
```{r, pkgs} 
library(FLCore) 
library(FLBRP)
library(FLasher)
library(FLife)
library(mydas)
library(ggplotFL) 

library(ggridges)
library(ggExtra)
library(ggside)
library(ggnewscale)
library(ggh4x)

library(viridis)

library(plyr)
library(dplyr)
library(reshape)
library(GGally)
library(ggpubr)

library(statcomp)
library(zoo)
library(Metrics)

library(popbio)

library(LBSPR)
library(spatstat)

library(readxl)

library(statcomp)

library(Metrics)

library(plotrix)
```


```{r, theme}
theme_custom<-function(sizeScale=1.0,angle.x=0){
  theme_bw() +
    theme(
      legend.position   ="bottom",
      legend.text       =element_text(size=sizeScale*12),
      legend.title      =element_text(size=sizeScale*16),
      axis.ticks        =element_line(         colour="grey70"),
      axis.text         =element_text(         colour="black"),
      axis.text.x       =element_text(size=sizeScale*12),
      axis.text.x.bottom=element_text(size=sizeScale*12,                         angle=angle.x,hjust=1), 
      axis.text.y       =element_text(size=sizeScale*12),
      axis.title.x      =element_text(size=sizeScale*16), 
      axis.title.y      =element_text(size=sizeScale*16),
      panel.border      =element_rect(         colour="black", fill=NA),
      panel.background  =element_rect(         colour =NA,     fill="white",),
      panel.grid.major  =element_line(         colour ="grey80"),
      panel.grid.minor  =element_line(         colour ="grey90"),
      strip.text.x      =element_text(size=sizeScale*16), 
      strip.text.y      =element_text(size=sizeScale*16),
      strip.background  =element_rect(                         fill="white"))}

theme_set(theme_custom())
```

```{r, source}
source("../R/skill.R")

# source("C:/flr/FLSkill/R/generics.R")
# source("C:/flr/FLSkill/R/plots.R")
# source("C:/flr/FLSkill/R/utils.R")
# source("C:/flr/FLSkill/R/classification.R")


tryIt<-function(x, silent=TRUE) {
  rtn=try(x, silent=silent)
  
  if ("try-error" %in% class(rtn)) 
    return(NULL)
  
  return(rtn)}

setGeneric("roc2", function(state, ind, ...) {
  standardGeneric("roc2")})

setMethod("roc2",
          signature(state = "numeric", ind = "numeric"),
          function(state, ind, ...) {
            order = order(ind, decreasing = TRUE)
            state = state[order]
            ind = ind[order]
            label = state > 1
            
            cumn = seq(1, length(label))
            
            TPR = cumsum(label) / sum(label)
            FPR = cumsum(!label) / sum(!label)
            
            TP = cumsum(label)
            FP = cumsum(!label)
            
            TN = sum(!label) - FP
            FN = sum(label) - TP
            
            TSS = (TP / (TP + FN) - FP / (FP + TN))
            
            result_df = data.frame(
              state = state,
              label = label,
              ind = ind,
              TPR = TPR,
              FPR = FPR,
              TP = TP,
              TN = TN,
              FP = FP,
              FN = FN,
              TSS = TSS,
              order = order
            )
            
            return(result_df)})
```

```{r}
species_colours=c("Sprat"="#1b9e77", 
                    "Turbot"="#d95f02", 
                    "Pollack"="#7570b3", 
                    "Bigeye"="#e7298a", 
                    "Ray"="#66a61e")
```

## Operating Model

```{r, oms}
load(file.path("../data/om","design.RData")) 
design=cbind(.id=seq(dim(design)[1]),design)
design=cbind(design,data.frame(Scenario=rep(c("Base Case","h=0.9","Domed","n=100","Low M","Immature"),15)))

spp=c("Pollack","Turbot","Ray","Sprat","Bigeye")
names(spp)=c("Pollachius pollachius","Psetta maxima","Raja clavata","Sprattus sprattus sprattus","Thunnus obesus")
  
design$Species=factor(design$Species,levels=c("Pollachius pollachius",
                                              "Psetta maxima",
                                              "Raja clavata",
                                              "Sprattus sprattus sprattus",
                                              "Thunnus obesus")[c(4,2,1,5,3)],
                               labels=c("Pollack","Turbot","Ray","Sprat","Bigeye")[c(4,2,1,5,3)])

main=seq(1,30,6)

load(file.path("../data/om","om.1.RData"))
oms=FLStocks(om)
eqs=FLBRPs(eq)

load(file.path("../data/om","om.7.RData"))
oms[[2]]=om
eqs[[2]]=eq

load(file.path("../data/om","om.13.RData"))
oms[[3]]=om
eqs[[3]]=eq

load(file.path("../data/om","om.19.RData"))
oms[[4]]=om
eqs[[4]]=eq

load(file.path("../data/om","om.25.RData"))
oms[[5]]=om
eqs[[5]]=eq

names(oms)=c("Pollack","Turbot","Ray","Sprat","Bigeye")
names(eqs)=c("Pollack","Turbot","Ray","Sprat","Bigeye")
oms=oms[c(4,2,1,5,3)]
eqs=eqs[c(4,2,1,5,3)]

save(oms,eqs,    file=file.path("../data/results","base.RData"))
save(design,main,file=file.path("../data/results","design.RData"))
```

```{r, lfds}
load(file.path("../data/om","lfd.1.RData"))
lfds=FLQuants(lfd)

load(file.path("../data/om","lfd.7.RData"))
lfds[[2]]=lfd

load(file.path("../data/om","lfd.13.RData"))
lfds[[3]]=lfd

load(file.path("../data/om","lfd.19.RData"))
lfds[[4]]=lfd

load(file.path("../data/om","lfd.25.RData"))
lfds[[5]]=lfd
names(lfds)=c("Pollack","Turbot","Ray","Sprat","Bigeye")
lfds=lfds[c(4,2,1,5,3)]

save(lfds,file=file.path("../data/results","lfds.RData"))

lmax=maply(data.frame(Species=names(lfds)), function(Species) max(an(dimnames(lfds[[Species]])[[1]])))[c(4,5,2,3,1)]

save(design,main,lmax,file=file.path("../data/results","design.RData"))
```

```{r, rfpts}
load(file.path("../data/om","design.RData"))

M=mdply(data.frame(.id=seq(dim(design)[1])), function(.id) { 
            load(file.path("../data/om",paste("om",.id,"RData",sep=".")))
            lh=lhs[[ac(design[.id,"Species"])]]
            
            data.frame(M=mean(m(eq)[ac(ceiling(lh["sel1"]):floor(vonB(length=lh["linf"]*0.9,params=lh)))]))})
save(M,file=file.path("../data/results","M.RData"))

ref=mdply(data.frame(.id=seq(dim(design)[1])), function(.id) { 
            load(file.path("../data/om",paste("om",.id,"RData",sep=".")))
  
            cbind(design[.id,],"M"=M[.id,"M"],model.frame(FLQuants(
                                 Fbar =fbar(iter(om,1)),
                                 Z    =fbar(iter(om,1))+M[.id,"M"],
                                 FFMSY=fbar(iter(om,1))%/%refpts(eq)["msy","harvest"]),drop=TRUE))})
save(ref,file=file.path("../data/results","ref.RData"))

msy=mdply(data.frame(.id=seq(dim(design)[1])), function(.id) {
  load(file.path("../data/om",paste("om",.id,"RData",sep=".")))
  fmsy =an(refpts(eq)["msy","harvest"]) 
  bmsy =an(refpts(eq)["msy","ssb"])
  b0   =an(refpts(eq)["virgin","ssb"])
  msy  =an(refpts(eq)["msy","yield"])
  shape=bmsy/b0

  lh=lhs[[ac(design[.id,"Species"])]]
  M =mean(m(eq)[ac(ceiling(lh["sel1"]):floor(vonB(length=lh["linf"]*0.9,params=lh)))])
  
  cbind(design[.id,],data.frame(M=M,msy=msy,bmsy=bmsy,fmsy=fmsy,hmsy=1-exp(-fmsy),b0=b0,shape=shape))})

save(msy,file=file.path("../data/results","msy.RData"))
```


```{r, lhat}
load(file.path("../data/results","design.RData"))
load(file.path("../data/results","M.RData"))
load(file.path("../data/results","ref.RData"))
load(file.path("../data/results","lbi.RData"))
load(file.path("../data/results","lime.RData"))
load(file.path("../data/results","lbspr.RData"))
load(file.path("../data/results","lbspr2.RData"))

lbi  =merge(lbi,   ref)
lime =merge(lime,  ref)
lbspr=merge(lbspr2,ref)

lhat=rbind(
     cbind(What="LCC Absolute"         ,transmute(lbi,  .id=.id,iter=as.integer(iter),year=as.integer(year),data=z)),
     cbind(What="LCC"        ,transmute(lbi,   .id=.id,iter=as.integer(iter),year=as.integer(year),data=(z-M)/M)),
     cbind(What="LCC Lmax Absolute"    ,transmute(lbi,
                                               .id=.id,iter=as.integer(iter),year=as.integer(year),data=as.numeric(z.lmax))),
     cbind(What="LCC Lmax"    ,transmute(lbi,  .id=.id,iter=as.integer(iter),year=as.integer(year),data=(as.numeric(z.lmax)-M)/M)),
     cbind(What="BH Absolute" ,transmute(lbi, 
                                               .id=.id,iter=as.integer(iter),year=as.integer(year),data=as.numeric(z.bh))),
     cbind(What="BH"          ,transmute(lbi,  .id=.id,iter=as.integer(iter),year=as.integer(year),data=(as.numeric(z.bh)-M)/M)),
     cbind(What="LIME"        ,transmute(lime, .id=.id,iter=as.integer(iter),year=as.integer(year),data=FFmsy)),
     cbind(What="LBSPR"       ,transmute(lbspr,.id=.id,iter=as.integer(iter),year=as.integer(year),data=fm)),
     cbind(What="1/Lmean"     ,transmute(lbi, 
                                         .id=.id,iter=as.integer(iter),year=as.integer(year),data=1/lmean)))
lhat=merge(lhat,design,by=".id")
l80 =ddply(subset(lhat,year%in% 79:81),  .(Species,Scenario,CV,iter,What), with,data.frame(l80 =mean(data)))
l115=ddply(subset(lhat,year%in%114:116), .(Species,Scenario,CV,iter,What), with,data.frame(l115=mean(data)))

lhat=merge(lhat,l80, by=c("Species","Scenario","CV","What","iter"))
lhat=merge(lhat,l115,by=c("Species","Scenario","CV","What","iter"))
lhat=subset(lhat,What%in%c("1/Lmean","LCC","BH","LBSPR","LIME"))
lhat$What=factor(lhat$What,levels=c("1/Lmean","LCC","BH","LBSPR","LIME")) 
lhat=subset(lhat,!is.na(data))
lhat=merge(lhat,ref[,c(".id","year","FFMSY")])

phat   =ddply(lhat, .(Species,Scenario,CV,What,year), with, quantile(data,     probs=c(0.025,0.25,0.5,0.75,0.975), na.rm=T))
prel   =ddply(lhat, .(Species,Scenario,CV,What,year), with, quantile(data/l80, probs=c(0.025,0.25,0.5,0.75,0.975), na.rm=T))
prel115=ddply(lhat, .(Species,Scenario,CV,What,year), with, quantile(data/l115,probs=c(0.025,0.25,0.5,0.75,0.975), na.rm=T))

save(lhat,phat,prel,prel115,file=file.path("../data/results","lhat.RData"))  
```


```{r, fig_2, fig.width=9,fig.height=8}
theme_set(theme_custom())

dat=transform(lh[,c(1:3,8,6)],linf=log(linf),k=log(k),l50=log(l50))
dat$Species=factor(dat$species,levels=c("Sprattus sprattus sprattus",
                                        "Psetta maxima",
                                        "Pollachius pollachius",
                                        "Thunnus obesus",
                                        "Raja clavata"),
                               labels=c("Pollack","\nBigeye","Turbot","\nSprat","Ray"))

my_smooth=function(data, mapping, ...) {
  ggplot(data=data, mapping=mapping) +
    geom_point(..., size=2.0, alpha=0.6) +
    geom_smooth(..., method="lm", se=FALSE, colour="grey50", linewidth=0.75)}

my_histogram=function(data, mapping, ...) {
  ggplot(data=data, mapping=mapping) +
    geom_histogram(..., colour="grey", alpha=1.80) + 
    theme(axis.text.y       =element_blank(),     
          axis.ticks.y      =element_blank(),    
          panel.grid.major.y=element_blank())}

fig_2=ggpairs(  
  dat[,-1],
  columnLabels=c("log(L[infinity])", "log(k)", "log(L[50])", "b", "Species"),
  labeller=label_parsed,
  mapping=ggplot2::aes(fill=Species, col=Species),
  lower=list(continuous=wrap(my_smooth)),
  upper=list(continuous=wrap(my_smooth)),
  diag=list(continuous=wrap(my_histogram)),
  title="Relationships between life history parameters")+
  scale_colour_viridis_d(option="D")+
  scale_fill_viridis_d( option="D") 

  fig_2[5, 1]=fig_2[5, 1]+ 
    theme(axis.text.y       =element_blank(),
          axis.ticks.y      =element_blank(),
          panel.grid.major.y=element_blank(),
          axis.text.x.bottom=element_text(angle=45))
  fig_2[5, 2]=fig_2[5, 2]+
    theme(axis.text.x.bottom=element_text(angle=45))
  fig_2[5, 3]=fig_2[5, 3]+
    theme(axis.text.x.bottom=element_text(angle=45))
  fig_2[5, 4]=fig_2[5, 4]+
    theme(axis.text.x.bottom=element_text(angle=45))
  fig_2[5, 5]=fig_2[5, 5]+
    theme(axis.text.x.bottom=element_text(hjust=0.5))
    
fig_2

ggsave(file.path("../tex/fig_2.png"), fig_2, width=9, height=8, dpi=300)
```

**Figure `r iFig=iFig+1; iFig`** Life history parameters and the correlations between them.

```{r, fig_3, fig.width=12,fig.height=6}
ymsy<-function(x) refpts(x)["msy","yield"] 
rmsy<-function(x) refpts(x)["msy","rec"]

mets=list(RMSY =function(x, y) rec(  x)/ rmsy(y),
             YMSY =function(x, y) catch(x)/ ymsy(y),
             SBMSY=function(x, y) ssb(  x)/sbmsy(y),
             FMSY =function(x, y) fbar( x)/ fmsy(y))

fqs=FLQuants(lapply(mets, function(m)
  dbind(FLQuants(Map(function(x, y) m(x, y), x=oms, y=eqs)), dim=3)))

fig_3=plot(fqs, iter="1", probs=c(0.025, 0.5, 0.975)) +
  ylim(c(0, NA))+
  geom_hline(aes(yintercept=1), linetype="dashed", colour="black", size=0.8)+
  facet_grid(factor(ac(qname), 
              levels=c("FMSY", "RMSY", "SBMSY", "YMSY"),
              labels=c(expression(F[MSY]), expression(R[MSY]), expression(SSB[MSY]),
                       expression(Y[MSY])))~unit,
    scale="free",labeller=label_parsed)+
  scale_x_continuous(limits=c(50, 120), breaks=seq(60, 120, by=20)) + # Add regular x-axis ticks
  theme_custom()+
  theme(legend.position="none")+
  scale_colour_manual(values=c("black","black","black","black","black","red"))+
  scale_fill_manual(values=rep("grey75",6))+
  #scale_fill_viridis_d( option="D") 
  labs(
    title="Operating Models",
    x="Year",
    y="",
    caption="Dashed line indicates MSY refererence level")
  
fig_3

ggsave(file.path("../tex/fig_3.png"), fig_3, width=12, height=6, dpi=300)
```

**Figure `r iFig=iFig+1; iFig`** Operating Models for Base Case.


## Observation Error Model
 
```{r, fig_4, fig.width=10,fig.height=5} 
load(file.path("../data/results","design.RData"))
load(file.path("../data/results","lfds.RData"))

lmodeFn<-function(len,n,bin=25) {
  
  dat=data.frame(bin=cut(len,breaks=bin),n=n)
  res=ddply(dat,.(bin), with, data.frame(freq=sum(n)))
  res=as.character(subset(res,freq==max(freq))[1,"bin"])
  unbin(res)$mid}

dat=subset(transform(ldply(lfds, as.data.frame),lustrum=5*(year%/%5)),year>=60) 
dat=subset(dat,lustrum%in%c(60,100, 120))

dt2=ddply(dat,.(.id,lustrum), with, {
  lc=lmodeFn(len,data)*0.5
  data.frame(lc   =lc,
             lmean=weighted.mean(len,data*(len>=lc)))})

#dat$lustrum=factor(ac(dat$lustrum), levels=ac(c(60,100,120)),labels=c("Initial","Overfished","Recovered"))
fig_4=ggplot(dat,aes(x=len,weight=data))+
  geom_histogram(bins=25,fill="grey75",col="grey10")+
  #coord_flip()+
  #scale_x_reverse()+
  facet_grid(lustrum~
             factor(.id,levels=c("Sprat","Turbot","Pollack","Bigeye","Ray")),scale="free")+
  #geom_vline(aes(xintercept=lc),    data=dt2,linetype=1)+
  geom_vline(aes(xintercept=lmean), data=dt2,col="blue")+
  theme_custom()+
  theme(legend.position="none", 
        axis.title.y=element_blank(), 
        axis.text.y =element_blank(), 
        axis.ticks.y=element_blank())+
  labs(title  ="Observation Error Model",
       x      ="Length (cm)",
       y      ="",
       caption=expression("Vertical line shows" ~ L[mean]))

fig_4

ggsave(file.path("../tex/fig_4.png"), fig_4, width=10, height=5, dpi=300)
```

**Figure `r iFig=iFig+1; iFig`** Length data

## Length based approaches

```{r, fig_5, fig.width=10, fig.height=8}
key=data.frame(What=c("1/Lmean","LCC","BH","LBSPR","LIME"),
               Type=c("Indicator","Legacy","Legacy","Modern","Modern"))

phat=merge(phat,key)

fig_5=ggplot(subset(phat,Scenario%in%"Base Case"))+  
  facet_nested(factor(Species,levels=c("Sprat","Turbot","Pollack","Bigeye","Ray"))~Type+What,
               scale="free", nest_line=TRUE, solo_line=TRUE,labeller=label_wrap_gen(width=10))+
  geom_ribbon(aes(year, ymin=`2.5%`, ymax=`97.5%`), alpha=0.3, fill="grey75") +
  geom_line(aes(year,y=`50%`)) +
  geom_smooth(aes(year, y=`2.5%`),  colour="grey10", linewidth=0.2, se=FALSE, span=0.1) + 
  geom_smooth(aes(year, y=`97.5%`), colour="grey10", linewidth=0.2, se=FALSE, span=0.2) + 
  geom_line(aes(year, y=`50%`),     colour="grey10", linewidth=0.5)+ 
  geom_line(aes(year, FFMSY, linetype=1, linewidth=0.8), 
            dat=subset(ref, .id %in% subset(design, Scenario=="Base Case" & CV==0.3)$.id)[,c("year","FFMSY")],
            colour="red", linewidth=0.8, linetype=1) +
  geom_hline(aes(yintercept=1, linetype="Target"), colour="darkred", size=0.6) + 
  xlab("Year") + ylab("Relative Fishing Pressure") +
  geom_vline(aes(xintercept=100), linetype="dashed") +
  scale_x_continuous(limits=c(60,120), breaks=seq(60,120,20))+
  coord_cartesian(ylim=c(0,3))+ 
  scale_linetype_manual(name="", 
                       values=c("Reference"=2, "Target"=1),
                       labels=c("Reference"="FMSY Reference", "Target"="Target Level"))+
  theme_custom()+
  theme(legend.position="bottom")  

ggsave(file.path("../tex/fig_5.png"), fig_5, width=12, height=8, dpi=300)
fig_5
```

**Figure `r iFig=iFig+1; iFig`.** Example of length based indicators and estimators for **Base Case by species**.


```{r, fig_5b, fig.width=10, fig.height=8}
fig_5b=ggplot(subset(phat,Species=="Pollack"))+  
  facet_nested(factor(Scenario,levels=c("Base Case","h=0.9","Low M","Domed","Immature","n=100"),
                             labels=c("Reference\nCase","h=0.9","Low M","Domed","Immature","n=100"))~
                 Type+What,
               scale="free", nest_line=TRUE, solo_line=TRUE,labeller=label_wrap_gen(width=10))+
  geom_ribbon(aes(year, ymin=`2.5%`, ymax=`97.5%`), alpha=0.3, fill="grey75") +
  geom_line(aes(year,y=`50%`)) +
  geom_smooth(aes(year, y=`2.5%`),  colour="grey10", linewidth=0.5, se=FALSE, span=0.1) + 
  geom_smooth(aes(year, y=`97.5%`), colour="grey10", linewidth=0.5, se=FALSE, span=0.2) + 
  geom_line(aes(year, y=`50%`),     colour="grey10", linewidth=0.8)+ 
  geom_line(aes(year, FFMSY, linetype="Reference"), 
            dat=subset(ref, .id %in% subset(design, Scenario=="Base Case" & CV==0.3)$.id)[,c("year","FFMSY")],
            colour="red", size=0.8) +
  geom_hline(aes(yintercept=1, linetype="Target"), colour="darkred", size=0.6) + 
  xlab("Year") + ylab("Relative Fishing Pressure") +
  geom_vline(aes(xintercept=100), linetype="dashed") +
  scale_x_continuous(limits=c(60,120), breaks=seq(60,120,20))+
  coord_cartesian(ylim=c(0,3))+ 
  scale_linetype_manual(name="", 
                       values=c("Reference"=2, "Target"=1),
                       labels=c("Reference"="FMSY Reference", "Target"="Target Level"))+
  theme_custom()+
  theme(legend.position="bottom")

fig_5b
```

**Figure `r iFig=iFig; iFig`.a.** Example of length based indicators and estimators for **pollack across scenarios**.

## Analysis

```{r, figRoc, fig.height=10,fig.width=10}
load(file.path("../data/results","lhat.RData"))

rocs=mdply(data.frame(Lag=0),function(Lag) {
  ddply(subset(lhat, year %in% 60:120 & !is.na(FFMSY) & !is.na(data)), .(Species,What,Scenario,CV), 
        function(x) {
          n=length(x$FFMSY)
          if(Lag==0) tryIt(rocFn(x$FFMSY>1,           x$data))
            else     tryIt(rocFn(x$FFMSY[1:(n-Lag)]>1,x$data[(Lag+1):n]))})})
rank=ddply(rocs, .(Species,What,Scenario,CV), with, auc(TPR,FPR)) 
rank=ddply(rank, .(What), with, mean(V1)) 
rocs=transform(rocs,Scenario=factor(Scenario,levels=c("Base Case","h=0.9","Low M","Domed","Immature","n=100"),
                                               labels=c("Reference","h=0.9","Low M","Domed","Immature","n=100")),
                      What    =factor(What,    levels=ac(rank[rev(order(rank[,2])),1]),
                                               labels=ac(rank[rev(order(rank[,2])),1])))

tss=ddply(subset(rocs, What%in%c("1/Lmean","LCC","BH","LBSPR","LIME")), 
          .(Species,Scenario,CV,What), with, data.frame(TPR=TPR[min(abs(ind-1))==abs(ind-1)][1],
                                                        FPR=FPR[min(abs(ind-1))==abs(ind-1)][1]))

ts2=mdply(data.frame(Lag=0),function(Lag) {
  ddply(subset(lhat, year %in% 60:120 & !is.na(FFMSY) & !is.na(data)), .(Species,What,Scenario,CV), 
        function(x) {
          n=length(x$FFMSY)
          if(Lag==0) tryIt(skillSummary( x$FFMSY>1,           x$data))
            else     tryIt(skillSummary( x$FFMSY[1:(n-Lag)]>1,x$data[(Lag+1):n]))})})

dat=subset(rocs,What%in%c("1/Lmean","LCC","BH","LBSPR","LIME"))
ggplot(dat)+
  geom_path( aes(FPR,TPR,group=paste(Scenario,CV)),col="grey")+
  geom_path( aes(FPR,TPR),data=subset(dat,Scenario=="Reference"&CV==0.3))+
  geom_point(aes(FPR,TPR),data=subset(tss,Scenario=="Reference"&CV==0.3),size=5)+
  geom_point(aes(FPR,TPR),data=tss,shape=21,size=2,fill="grey")+
  geom_point(aes(FPR,TPR),data=ts2,size=2,col="blue")+
  geom_abline(aes(slope=1,intercept=0),linetype=2)+
  facet_grid(factor(What,levels=c("1/Lmean","LCC","BH","LBSPR","LIME"))~Species)+
  theme_custom()+
  theme(legend.position="bottom")+
  scale_x_continuous(breaks=c(  0.5,1))+
  scale_y_continuous(breaks=c(0,0.5,1)) 
```

**Figure `r iFig=iFig+1; iFig`.** ROC curves with reference level indicated.

```{r, skill}
load(file.path("../data/results","lhat.RData"))

x=subset(lhat,Scenario==unique(Scenario)[1]&What==unique(What)[1]&
              Species ==unique(Species)[1]&CV==unique(CV)[1]&iter==1)

skill=mdply(data.frame(Lag=0:5),function(Lag) {
  ddply(subset(lhat, year %in% 60:120 & !is.na(FFMSY) & !is.na(data)), .(Species,What,Scenario,CV,iter), 
        function(x) {
          n=length(x$FFMSY)
          if(Lag==0) tryIt(skillSummary( x$FFMSY>1,           x$data))
            else     tryIt(skillSummary( x$FFMSY[1:(n-Lag)]>1,x$data[(Lag+1):n]))})})
rank=ddply(skill,.(What), with,  data.frame(score=mean(AUC,na.rm=TRUE)))  
skill=transform(skill,Scenario=factor(Scenario,levels=c("Base Case","h=0.9","Low M","Domed","Immature","n=100"),
                                               labels=c("Reference","h=0.9","Low M","Domed","Immature","n=100")),
                      What    =factor(What,    levels=ac(rank[rev(order(rank[,2])),1]),
                                               labels=ac(rank[rev(order(rank[,2])),1]))) 

save(skill,lhat,file=file.path("../data/results","skill.RData"))
```

```{r, lag}
rank=ddply(skill,.(What,Species,Lag), with,  data.frame(score=mean(AUC,na.rm=TRUE)))  

ggplot(rank)+
  geom_point(aes(Lag,score))+
  facet_grid(Species~What) 
```

```{r, fig_7, fig.height=10,fig.width=16}
dat=ddply(subset(skill,Lag==1), .(Species,What,Scenario,CV,Lag), with, data.frame(AUC=median(AUC,na.rm=TRUE))) 

rank=ddply(skill,.(What), with,  data.frame(score=median(AUC,na.rm=TRUE)))  
dat =transform(dat,What=factor(What,levels=ac(rank[rev(order(rank[,"score"])),1]),
                                              labels=ac(rank[rev(order(rank[,"score"])),1])))
  
fig_7=ggplot(dat) + 
  geom_rect(data=aucCat, 
            aes(xmin=xmin, xmax=6.5, ymin=ymin, ymax=ymax, fill=quality),
            alpha=0.75) +  
  geom_point(aes(x=Scenario, y=AUC, col=Scenario), size=3) +
  geom_hline(aes(yintercept=AUC), col="blue", data=subset(dat, Scenario=="Reference")) +
  facet_nested(Species~What+CV, nest_line=TRUE, solo_line=TRUE) +
  ylab("AUC (Area Under the Receiver Operating Characteristic Curve)") +
  xlab("Simulation Scenario") +
  geom_hline(aes(yintercept=y),linewidth=0.3,data=data.frame(y=c(0.6,0.7,0.9)))+
  scale_y_continuous(limits=c(0.4,1.02), breaks=c(0.6,0.7,0.9))+
  scale_fill_manual(values=aucCol) +
  scale_colour_viridis_d(option="C", end=0.9)+
  theme_custom(angle.x=45)+
  theme(legend.position="bottom")

fig_7

ggsave(file.path("../tex/fig_7.png"), fig_7, width=14, height=10, dpi=300)
```

**Figure `r iFig=iFig+1; iFig`.** Summary of area under the ROC curves

```{r, bias, fig.width=10, fig.height=12}
ggplot(data=skill)+ 
  facet_grid(Species~What,scale="free", labeller=label_parsed)+
  geom_density_ridges_gradient(
                    aes(x=ref, y=Scenario, fill=stat(x)),
                    adjust=0.2,
                    rel_min_height=0.01,
                    bandwidth=0.1,
                    quantile_lines=TRUE,
                    quantiles=c(0.5),
                    alpha=0.6, scale=2)+
  scale_x_continuous(limits=c(0,3.0),breaks=c(0,1,2))+
  scale_fill_gradientn("",colours=c("orange", "green","orange"),
                       values=scales::rescale(c(0, 0.9, 1.1, 3)))+
  geom_vline(aes(xintercept=1.0), linetype="solid", col="blue",size=1)+
  theme_ridges()+
  labs(x="Ratio", 
       y="Scenario")+
  theme_custom(0.8)+
  theme(legend.position="bottom",
        panel.spacing=unit(0.1, "lines")) 
```

**Figure `r iFig=iFig+1; iFig`.** Bias

```{r, skill2}
#dat=subset(lhat, year %in% 60:120 & !is.na(FFMSY) & !is.na(data)&Species=="Sprat"&What=="1/Lmean"&CV==0.3&Scenario=="h=0.9"&iter==1)

skill2=mdply(data.frame(Lag=0:5),function(Lag) {
  ddply(subset(lhat, year %in% 60:120 & !is.na(FFMSY) & !is.na(data)), .(Species,What,Scenario,CV,iter), 
        function(x) {
          n=length(x$FFMSY)
          if(Lag==0) tryIt(skillSummary( x$FFMSY>1,           x$data,           reference=1))
            else     tryIt(skillSummary( x$FFMSY[1:(n-Lag)]>1,x$data[(Lag+1):n],reference=1))})})
rank2=ddply(skill2,.(What), with,  data.frame(score=mean(AUC,na.rm=TRUE)))  
skill2=transform(skill2,
                 Scenario=factor(Scenario,levels=c("Base Case","h=0.9","Low M","Domed","Immature","n=100"),
                                          labels=c("Reference","h=0.9","Low M","Domed","Immature","n=100")),
                 What    =factor(What,    levels=ac(rank[rev(order(rank[,2])),1]),
                                          labels=ac(rank[rev(order(rank[,2])),1])))
```

```{r, fig_8a, fig.width=12, fig.height=12}
dat=ddply(skill2, .(Scenario,Species,What,CV), with, data.frame(TSS=median(TSS,na.rm=TRUE)))

dt2=subset(dat,Scenario=="Reference"&CV==0.3&What%in%c("LBSPR","1/Lmean"))
dt2$Scenario=ac(dt2$Scenario)
dt3=subset(dat,Scenario=="Reference"&What%in%c("LBSPR","1/Lmean"))
dt2$Scenario=ac(dt2$Scenario)
dt2=merge(dt3[,c("Species","Scenario","CV","What")],
          dt2[,c("Species","Scenario","What","TSS")],all.x=TRUE)

theme_set(theme_custom())
fig_8a=ggplot(subset(dat,What%in%c("LBSPR","1/Lmean")))+ 
  geom_rect(data=tssCat, 
            aes(xmin=xmin, xmax=6.5, ymin=ymin, ymax=ymax, fill=quality),
            alpha=0.75)+
  geom_point(aes(x=Scenario,TSS,col=Scenario),size=4)+
  facet_nested(Species~What+CV, nest_line=TRUE, solo_line=TRUE)+
  geom_hline(aes(yintercept=TSS),col="blue",data=dt2)+
  geom_hline(aes(yintercept=y),linewidth=0.3,data=data.frame(y=c(0.0,0.2,0.4,0.6)))+
  ylab("TSS")+
  scale_y_continuous(limits=c(-0.4,1.1), breaks=c(0.0,0.2,0.4,0.6))+
  scale_fill_manual("Skill",values=tssCol)+
  scale_colour_viridis_d(option="C",end=0.9)+  
      labs(title="Proxies", x="", y="")+
  theme_custom()+
  theme(axis.text.x.bottom=element_blank()) 
      
fig_8a
```

**Figure `r iFig=iFig+1; iFig`.** True Skill Score, analytically 


```{r, fig_8b, fig.width=12, fig.height=12}
load(file.path("../data/results","skill.RData"))

dat=ddply(skill, .(Scenario,Species,What,CV), with, data.frame(TSS=median(TSS,na.rm=TRUE)))

#dat$Scenario=factor(dat$Scenario,levels=c("Base Case","h=0.9","Low M","Domed","Immature","n=100"),
#                                 labels=c("Reference","h=0.9","Low M","Domed","Immature","n=100"))

dt2=subset(dat,Scenario=="Reference"&CV==0.3&What%in%c("LBSPR","1/Lmean"))
dt2$Scenario=ac(dt2$Scenario)
dt3=subset(dat,Scenario=="Reference"&What%in%c("LBSPR","1/Lmean"))
dt2$Scenario=ac(dt2$Scenario)
dt2=merge(dt3[,c("Species","Scenario","CV","What")],
          dt2[,c("Species","Scenario","What","TSS")],all.x=TRUE)

fig_8b=ggplot(subset(dat,What%in%c("LBSPR","1/Lmean")))+ 
  geom_rect(data=tssCat, 
            aes(xmin=xmin, xmax=6.5, ymin=ymin, ymax=ymax, fill=quality),
            alpha=0.75)+
  geom_point(aes(x=Scenario,TSS,col=Scenario),size=4)+
  facet_nested(Species~What+CV, nest_line=TRUE, solo_line=TRUE)+
  geom_hline(aes(yintercept=TSS),col="blue",data=dt2)+
  geom_hline(aes(yintercept=y),linewidth=0.3,data=data.frame(y=c(0.0,0.2,0.4,0.6)))+   
  ylab("TSS")+
  scale_y_continuous(limits=c(-0.4,1.1), breaks=c(0.0,0.2,0.4,0.6))+
  scale_fill_manual("Skill",values=tssCol)+
  scale_colour_viridis_d(option="C",end=0.9)+  
      labs(title="Calibrated", x="", y="")+
  theme_custom()+
  theme(axis.text.x.bottom=element_blank()) 
  
fig_8b
```

**Figure `r iFig=iFig+1; iFig`.** True Skill Score, tuned


```{r, trend}
trend3=ddply(subset(lhat,year%in%90:110,!is.na(FFMSY)&!is.na(data)), 
             .(Species,What,Scenario,CV,iter), with, 
        data.frame(om=diff(rollmean(FFMSY,3)), mp=diff(rollmean(data,3))))

trend5=ddply(subset(lhat,year%in%90:110,!is.na(FFMSY)&!is.na(data)), 
             .(Species,What,Scenario,CV,iter), with, 
        data.frame(om=diff(rollmean(FFMSY,5)), mp=diff(rollmean(data,5))))

save(trend3,file=file.path("../data/results","trend3.RData"))
save(trend5,file=file.path("../data/results","trend5.RData"))
```


```{r, fig.width=12, fig.height=12}
load(file.path("../data/results","skill.RData"))

tss=ddply(subset(skill, Lag==1&What%in%c("1/Lmean","LCC","BH","LBSPR","LIME")), 
          .(Species,Scenario,CV,What,iter), with, data.frame(TSS=TSS[min(abs(ref-1))==abs(ref-1)][1]))
tss$Scenario=factor(tss$Scenario,levels=c("Base Case","h=0.9","Low M","Domed","Immature","n=100"),
                    labels=c("Reference","h=0.9","Low M","Domed","Immature","n=100"))
rank=ddply(tss,.(What), with,  
  data.frame(score=mean(TSS,na.rm=TRUE)))  
tss$What=factor(tss$What,levels=ac(rank[rev(order(rank[,2])),1]),
                         labels=ac(rank[rev(order(rank[,2])),1]))

 ggplot(tss)+
  geom_boxplot(aes(x=Scenario,
                   TSS,fill=CV),outlier.shape=NA)+
  geom_boxplot(aes(x=Scenario,
                   TSS,fill=CV),outlier.shape=NA)+
  geom_hline(aes(yintercept=0.0),linetype=1)+ 
  geom_hline(aes(yintercept=0.5),linetype=2)+ 
  facet_grid(What~Species)+
  ylab("TSS")+
  scale_y_continuous(limits=c(-0.25,1), breaks=c(0,0.5,1))+
  scale_fill_manual(values=c("blue","white","red"))+
  theme_custom(angle.x=45)
```

**Figure `r iFig=iFig+1; iFig`.** True Skill Score, analytically

```{r, fig.width=12, fig.height=12}
skill2=ddply(subset(lhat,year%in%60:120,!is.na(FFMSY)&!is.na(data/l115)), 
             .(Species,What,Scenario,CV,iter), with, tryIt(rocFn(FFMSY>1,data/l115))) 
skill2=transform(skill2,TSS=TPR-FPR)

tss=ddply(subset(skill2, What%in%c("1/Lmean","LCC","BH","LBSPR","LIME")), 
          .(Species,Scenario,CV,What,iter), with, data.frame(TSS=TSS[min(abs(ind-1))==abs(ind-1)][1]))
tss$Scenario=factor(tss$Scenario,levels=c("Base Case","h=0.9","Low M","Domed","Immature","n=100"),
                                 labels=c("Reference","h=0.9","Low M","Domed","Immature","n=100"))
rank=ddply(tss,.(What), with,  
  data.frame(score=mean(TSS,na.rm=TRUE)))  
tss$What=factor(tss$What,levels=ac(rank[rev(order(rank[,2])),1]),
                         labels=ac(rank[rev(order(rank[,2])),1]))

ggplot(tss)+  
  geom_boxplot(aes(x=Scenario,TSS,fill=CV),outlier.shape=NA)+
  geom_boxplot(aes(x=Scenario,TSS,fill=CV),outlier.shape=NA)+
  geom_hline(aes(yintercept=0.0),linetype=1)+ 
  geom_hline(aes(yintercept=0.5),linetype=2)+ 
  facet_grid(What~Species)+
  ylab("TSS")+
  theme_custom(angle.x=45)+
  scale_y_continuous(limits=c(-0.25,1), breaks=c(0,0.5,1))+
  scale_fill_manual(values=c("blue","white","red"))+  
      labs(title="", x="", y="")
```

**Figure `r iFig=iFig+1; iFig`.** True Skill Score, relative, 115

```{r, fig_8-110, fig.width=12, fig.height=12}
dat=ddply(tss,  .(Scenario,Species,What,CV), with, data.frame(TSS=median(TSS,na.rm=TRUE))) 

dt2=subset(dat,Scenario=="Reference Case"&CV==0.3&What%in%c("LBSPR","1/Lmean"))
dt2$Scenario=ac(dt2$Scenario)
dt3=subset(dat,Scenario=="Reference Case"&What%in%c("LBSPR","1/Lmean"))
dt2$Scenario=ac(dt2$Scenario)


dt2=merge(dt3[,c("Species","Scenario","CV","What")],
          dt2[,c("Species","Scenario","What","TSS")],all.x=TRUE)

ggplot(subset(dat,What%in%c("LBSPR","1/Lmean")))+ 
  geom_rect(data=tssCat, 
            aes(xmin=xmin, xmax=6.5, ymin=ymin, ymax=ymax, fill=quality),
            alpha=0.75)+
  geom_point(aes(x=Scenario,TSS,col=Scenario),size=4)+
  facet_nested(Species~What+CV, nest_line=TRUE, solo_line=TRUE)+
  #geom_hline(aes(yintercept=0.0),linetype=1)+ 
  geom_hline(aes(yintercept=y),linewidth=0.3,data=data.frame(y=c(0.0,0.2,0.4,0.6)))+
  geom_hline(aes(yintercept=TSS),col="blue",data=dt2)+
  theme_custom()+
  theme(axis.text.x.bottom=element_blank())+
  ylab("TSS")+
  scale_y_continuous(limits=c(-0.4,1.1), breaks=c(0.0,0.2,0.4,0.6))+
  scale_fill_manual("Skill",values=tssCol)+
  scale_colour_viridis_d(option="C",end=0.9)+  
      labs(title="", x="", y="")
```

**Figure `r iFig=iFig+1; iFig`.** True Skill Score, relative, 115


```{r, fig.width=12, fig.height=12}
skill3=ddply(subset(lhat,year%in%60:120,!is.na(FFMSY)&!is.na(data/l80)), 
             .(Species,What,Scenario,CV,iter), with, tryIt(rocFn(FFMSY>1,data/l80))) 
skill3=transform(skill3,TSS=TPR-FPR)

tss=ddply(subset(skill3, What%in%c("1/Lmean","LCC","BH","LBSPR","LIME")), 
          .(Species,Scenario,CV,What,iter), with, data.frame(TSS=TSS[min(abs(ind-1))==abs(ind-1)][1]))
tss$Scenario=factor(tss$Scenario,levels=c("Base Case","h=0.9","Low M","Domed","Immature","n=100"),
                                 labels=c("Reference","h=0.9","Low M","Domed","Immature","n=100"))
rank=ddply(tss,.(What), with,  
  data.frame(score=mean(TSS,na.rm=TRUE)))  
tss$What=factor(tss$What,levels=ac(rank[rev(order(rank[,2])),1]),
                         labels=ac(rank[rev(order(rank[,2])),1]))

ggplot(tss)+  
  geom_boxplot(aes(x=Scenario,TSS,fill=CV),outlier.shape=NA)+
  geom_boxplot(aes(x=Scenario,TSS,fill=CV),outlier.shape=NA)+
  geom_hline(aes(yintercept=0.0),linetype=1)+ 
  geom_hline(aes(yintercept=y),linewidth=0.3,data=data.frame(y=c(0.0,0.2,0.4,0.6)))+   
  geom_hline(aes(yintercept=TSS),col="blue",data=
               subset(dat,Scenario=="Reference Case"&CV==0.3&What%in%c("LBSPR","1/Lmean"))[,c(2,3,5)])+
  facet_grid(What~Species)+
  ylab("TSS")+
  theme_custom(angle.x=45)+
  scale_y_continuous(limits=c(-0.25,1), breaks=c(0,0.5,1))+
  scale_fill_manual(values=c("blue","white","red"))
```

**Figure `r iFig=iFig+1; iFig`.** True Skill Score, relative, 80

```{r, fig_8c, fig.width=12, fig.height=12}
dat=ddply(tss,  .(Scenario,Species,What,CV), with, data.frame(TSS=median(TSS,na.rm=TRUE))) 


dt2=subset(dat,Scenario=="Reference Case"&CV==0.3&What%in%c("LBSPR","1/Lmean"))
dt2$Scenario=ac(dt2$Scenario)
dt3=subset(dat,Scenario=="Reference Case"&What%in%c("LBSPR","1/Lmean"))
dt2$Scenario=ac(dt2$Scenario)


dt2=merge(dt3[,c("Species","Scenario","CV","What")],
          dt2[,c("Species","Scenario","What","TSS")],all.x=TRUE)

fig_8c=ggplot(subset(dat,What%in%c("LBSPR","1/Lmean")))+ 
  geom_rect(data=tssCat, 
            aes(xmin=xmin, xmax=6.5, ymin=ymin, ymax=ymax, fill=quality),
            alpha=0.75)+
  geom_point(aes(x=Scenario,TSS,col=Scenario),size=4)+
  facet_nested(Species~What+CV, nest_line=TRUE, solo_line=TRUE)+
  #geom_hline(aes(yintercept=0.0),linetype=1)+ 
  geom_hline(aes(yintercept=y),linewidth=0.3,data=data.frame(y=c(0.0,0.2,0.4,0.6)))+   
  geom_hline(aes(yintercept=TSS),col="blue",data=dt2)+
  ylab("TSS")+
  scale_y_continuous(limits=c(-0.4,1.1), breaks=c(0.0,0.2,0.4,0.6))+
  scale_fill_manual("Skill",values=tssCol)+
  scale_colour_viridis_d(option="C",end=0.9)+  
      labs(title="Reference Year", x="", y="")+
  theme_custom()+
  theme(axis.text.x.bottom=element_blank()) 
  
fig_8c
```

**Figure `r iFig=iFig+1; iFig`.** True Skill Score, relative, 80


```{r, fig_8d, fig.width=12, fig.height=12}
load(file.path("../data/results","trend3.RData"))
load(file.path("../data/results","trend5.RData"))

auc=ddply(trend3,.(Species,What,Scenario,CV), with,  
  data.frame(auc=pROC:::auc(om>0,mp)))

tss=ddply(subset(trend3,
                     What%in%c("LCC","BH","LIME","LBSPR","1/Lmean")),
           .(Species,Scenario,CV,What,iter), with,  {
 rtn=data.frame(roc2(om+1,mp+1))
 
 #data.frame(tss=with(rtn[abs(rtn$reference-1)==min(abs(rtn$reference-1)),],TPR-FPR))
 
 with(rtn, data.frame(
   tss    =(TPR-FPR)[abs(ind-1)==min(abs(rtn$ind-1))][1],
   tss.opt=ind[max(TPR-FPR)==TPR-FPR][1],
   ref.opt=max(TPR-FPR)))
 })

tss$Scenario=factor(tss$Scenario,levels=c("Base Case","h=0.9","Low M","Domed","Immature","n=100"),
                                 labels=c("Reference","h=0.9","Low M","Domed","Immature","n=100"))

dat=ddply(tss,  .(Scenario,Species,What,CV), with, data.frame(TSS=median(tss.opt,na.rm=TRUE)))

dt2=subset(dat,Scenario=="Reference Case"&CV==0.3&What%in%c("LBSPR","1/Lmean"))
dt2$Scenario=ac(dt2$Scenario)
dt3=subset(dat,Scenario=="Reference Case"&What%in%c("LBSPR","1/Lmean"))
dt2$Scenario=ac(dt2$Scenario)

dt2=merge(dt3[,c("Species","Scenario","CV","What")],
          dt2[,c("Species","Scenario","What","TSS")],all.x=TRUE)

fig_8d=ggplot(subset(dat,What%in%c("LBSPR","1/Lmean")))+ 
  geom_rect(data=tssCat, 
            aes(xmin=xmin, xmax=6.5, ymin=ymin, ymax=ymax, fill=quality),
            alpha=0.75)+
  geom_point(aes(x=Scenario,TSS,col=Scenario),size=4)+
  facet_nested(Species~What+CV, nest_line=TRUE, solo_line=TRUE)+
  geom_hline(aes(yintercept=y),linewidth=0.3,data=data.frame(y=c(0.0,0.2,0.4,0.6)))+   
  geom_hline(aes(yintercept=TSS),col="blue",data=dt2)+
  ylab("TSS")+
  scale_y_continuous(limits=c(-0.4,1.1), breaks=c(0.0,0.2,0.4,0.6))+
  scale_fill_manual("Skill",values=tssCol)+
  scale_colour_viridis_d(option="C",end=0.9)+  
      labs(title="Trend", x="", y="")+
  theme_custom()+
  theme(axis.text.x.bottom=element_blank()) 
  
fig_8d
```

**Figure `r iFig=iFig+1; iFig`.** True Skill Score, trend 5 years


```{r, fig_8, fig.width=12, fig.height=12}
fig_8a=fig_8a+theme( 
    axis.title.x = element_blank(),      
    axis.text.x  = element_blank(),      
    axis.ticks.x = element_blank(),      
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank())
fig_8b=fig_8b+theme(
    axis.title.x = element_blank(),      
    axis.text.x  = element_blank(),      
    axis.ticks.x = element_blank(),      
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank())
fig_8c=fig_8c+theme(
    axis.title.x = element_blank(),      
    axis.text.x  = element_blank(),      
    axis.ticks.x = element_blank(),      
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank())
fig_8d=fig_8d+theme(
    axis.title.x = element_blank(),      
    axis.text.x  = element_blank(),      
    axis.ticks.x = element_blank(),      
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank())

fig_8=ggarrange(fig_8a,fig_8c,fig_8b,fig_8d, common.legend=TRUE)

ggsave(file.path("../tex/fig_8.png"), fig_8, width=12, height=12, dpi=300)
```


```{r, fig.width=12,fig.height=4}
load(file.path("../data/results","lhat.RData")) 

source("../R/skill.R")

theme_set(theme_custom()) 

object=subset(lhat,Species=="Pollack"&CV==0.3&Scenario=="Base Case"&What=="LBSPR"&iter%in%1:5)

set.seed(6876)
object$FFMSY=object$FFMSY*rlnorm(length(object$FFMSY),0,0.2)

comp=skillPlot(subset(object,data>0.1),"FFMSY","data")

comp

ggsave(file.path("../tex/fig_6.png"), comp, width=12, height=4, dpi=300)
```

# References {#References}

## Author information

**Laurence Kell**. laurie@seaplusplus.co.uk

## Acknowledgements

## Software Versions

* `r version$version.string`
* FLCore:    `r packageVersion('FLCore')`
* FLBRP:     `r packageVersion('FLBRP')`
* FLasher:   `r packageVersion('FLasher')`
* FLife:     `r packageVersion('FLife')`
* mydas:     `r packageVersion('mydas')`
* **Compiled**: `r date()`

